Normal States Training for High Accuracy Event Detection

### 2016-07-19 paper/ieeeFormat.tex
format table

@@

\section{Proposed Method}
\begin{table}
\begin{tabular}{|p{0.1\columnwidth}|p{0.8\columnwidth}|} \hline
\(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \hline
\(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \hline
\(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \hline
\(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \hline
\(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \hline
\(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
\(\lambda\) & normal state weight in  NS-Prior-LDA\\ \hline
\(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \hline
\(S_c\) & topic \(c\)'s all normal states related words \\ \hline
\(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
\(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \hline
\(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \hline
\(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \hline
\(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \hline
\(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline

@@

\subsection{Initialization of Normal States}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
\begin{algorithm}
\caption{Normal States Initialization from Knowledge Base}
\label{alg:normalStatesInit}

>>>>

\usepackage{multirow}% for table

@@

\section{Proposed Method}
\begin{table}
\begin{tabular}{|c|p{0.1\columnwidth}|p{0.55\columnwidth}|} \hline
%first part: normalization initialization
\multirow{5}{0.18\columnwidth}{Normalization Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
& \(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \cline{2-3}
& \(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \cline{2-3}
& \(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \cline{2-3}
& \(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \cline{2-3}
& \(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
%second part: normalization maintenance
\multirow{4}{0.18\columnwidth}{Normalization Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
& \(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \cline{2-3}
& \(S_c\) & topic \(c\)'s all normal states related words \\ \cline{2-3}
& \(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
%third part: event detection
\multirow{5}{0.18\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \cline{2-3}
& \(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \cline{2-3}
& \(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \cline{2-3}
& \(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \cline{2-3}
& \(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline

@@

\subsection{Normal States Initialization}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
\begin{algorithm}
\caption{Normal States Initialization from Knowledge Base}
\label{alg:normalStatesInit}
